### 2016-05-03 ch03-lrm/truncation.tex
More small things
Improve structure in CH03, add workflow figure

The main contribution of this section is to come up with an improved \gls{FRF} by developing a method for smoothing the \gls{FRF} estimated via the \gls{LPM}. 
This is done by truncating the associated impulse response, as in~\citet{Schoukens1998}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the \gls{LPM} for leakage reduction. 
The truncation point (cut-off index) is determined by one of two statistically inspired methods.
It is then shown that a smooth \gls{LPM} estimate of the \gls{FRF} lowers the variance, thus improving the assessment level of the dynamic properties of a given \gls{LTI} system.
It should be noted, however, that such smoothing is merely of importance when inspecting the \gls{FRF} visually.
In particular, a slight bias is incurred when smoothing the \gls{FRF}.
If one is to fit a parametric model to the smoothed \gls{FRF}, one essentially ends up with a biased model (which is often undesirable).

@@

% The values $R = 2$, and $n=R+1=3$ will be used in the \gls{LPM}.
In this section, the $\lpm{3,2,2}$ is used.

@@

\subsection{Smoothing the \gls{FRF} estimate}
\label{sec:nparam:trunc:smoothingFRFestimate}
The method for smoothing (improving) the \gls{LPM} estimate of the frequency response function  is presented in this section together with pertinent assumptions. 
After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{{\LPM}}(\omega_k)$) from \secref{sec:nparam:LPM}, the smoothing method is decomposed into the following procedures, which will be elaborated on later:
\begin{enumerate}
\item The impulse response $\hat g_{\LPM}(t)$  is computed from the \gls{IDFT} of $\hat{G}_{{\LPM}}(\omega_k)$.

@@

\item An accurate estimate of the \gls{DC} value of the \gls{FRF} is computed by inspecting the average value of the tail of the estimated impulse response.

\item A truncation is effected at the point beyond which the data record (impulse response) is buried in noise.
This action results in smoothing the \gls{LPM} estimate of the \gls{FRF}.
\end{enumerate}

>>>>

The main contribution of this section is to come up with an improved \gls{FRF} by developing a method for smoothing the \gls{FRF} estimated via the \gls{LPM}. 
The smoothing of the \gls{FRF} happens by truncating the associated impulse response, as in~\citet{Schoukens1998}, but with the following additional extension: the determination of the optimal truncation time, without any user interaction, in conjunction with the use of the \gls{LPM} for leakage reduction. 
The truncation point (cut-off index) is determined by one of two statistically inspired methods.
It is then shown that a smooth \gls{LPM} estimate of the \gls{FRF} lowers the variance, thus improving the assessment level of the dynamic properties of a given \gls{LTI} system.
It should be noted, however, that such smoothing is merely of importance when inspecting the \gls{FRF} visually.
In particular, a slight bias might be incurred when smoothing the \gls{FRF}.
If one is to fit a parametric model to the smoothed \gls{FRF}, one essentially ends up with a biased model (which is often undesirable).

@@

% The values $R = 2$, and $n=R+1=3$ will be used in the \gls{LPM}.
In this section, the $\lpm{3,2,2}$ is used.
However, since the techniques discussed in this section are not specifically geared towards the \gls{LPM}, one can just as well use the concepts with other non-parametric \gls{FRF} estimators such as the \gls{LRM}.

@@

\subsection{Smoothing the \glsentryshort{FRF} estimate}
\label{sec:nparam:trunc:smoothingFRFestimate}
The method for smoothing (improving) the \gls{LPM} estimate of the frequency response function  is presented in this section together with pertinent assumptions.
After obtaining the \gls{LPM} estimate of the \gls{FRF} (denoted as $\hat{G}_{{\LPM}}(\omega_k)$) from \secref{sec:nparam:LPM}, the smoothing method is decomposed into the following procedures (see \figref{fig:nparam:truncation:workflow}), which will be elaborated on later:
\begin{enumerate}
\item The impulse response $\hat g_{\LPM}(t)$  is computed from the \gls{IDFT} of $\hat{G}_{{\LPM}}(\omega_k)$.

\item An accurate estimate of the \gls{DC} value of the \gls{FRF} is computed by inspecting the average value of the tail of the estimated impulse response and this is subtracted from the impulse response.

\item From the estimated impulse response $\hat{g}(t)$, the noise floor is estimated.

@@

\item A truncation is effected at the point beyond which the estimated impulse response is buried in noise.
This action results in smoothing of the \gls{FRF} when the truncated impulse response is transformed to the frequency domain using the \gls{DFT}.
\end{enumerate}

\begin{figure}
   \centering
   \setlength{\figurewidth}{0.75\columnwidth}
   \includegraphics[width=\figurewidth]{\thisDir/figs/workflow-truncation.pdf}
   \caption{Workflow for impulse response truncation.}
   \label{fig:nparam:truncation:workflow}
 \end{figure}
